### 2016-12-14 BF_correctness.tex
Continuing my pass...

Note that $\game{4}(A)=1$ iff there are~$r$ queries to the
$\HashOracle$ oracle that increment~$\err$, i.e., queries $y \not\in
S$ such that $\bigwedge_{j=1}^{k} M[v_j]=1$.
%We can assume without
%loss of generality that~$A$ does not call~$\HashOracle$ on $y \in S$
%because the indices $v_1,v_2,\ldots,v_k$ that will correspond to any
%$y \not\in S$ will be \emph{independent} of those corresponding to
%any of the $y \in S$. Thus these queries are wasted.
There are at total of $q_T + q_H$ queries made to~$\HashOracle$,
either directly by~$A$ or indirectly when~$A$ calls~$\TestOracle$.
For $\game{4}(A)$ to return~1, there must be~$r$ among these that
increment~$\err$. %We can assume without loss of generality that~$A$
%halts as soon as~$\err=r$ (which it can easily track), so
There are $\binom{q_T+q_H}{r}$ possible ``winning'' query patterns
to consider.  \jnote{I changed the bound; I don't think it was
correct before.} As each error event is independent of all previous
choices made by the~$\HashOracle$, we need only consider the
probability of a single error. Using the upper bound on false
positives for the classical Bloom filter shown by Kirsch and
Mitzenmacher~\cite{kirsch2006less}, we have $\Prob{\game{4}(A)=1}
\leq \binom{q_T+q_H}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
We conclude that
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,,
\]
as claimed.
\begin{figure}[tp]
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{$\game{4}(A)$} \\ %\fbox{$\game{5}(A)$}}\\
$S \getsr A$; $\err \gets 0$;  $\calC \gets \emptyset$\\
%$\mathcal{I}\getsr [\{1,2,\ldots,q_T+q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
%if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(q_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
Return $\Ans[x]$\\
%
}
{
\oracle{$\HashOracle(y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
%\nudge $c \gets c + 1$\\
%\nudge for $j \in \{1,2,\ldots,k\}$\\
%\nudge $v_j \getsr [m]$\\
%
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[v_j] \neq 1$ then \\
\nudge \nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
%\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge \nudge Return $\left(v_1,\ldots,v_k\right)$\\
%\nudge \nudge $\Break$\\
%if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
%if $c \notin \calI$ then $\bad \gets \true$\\
if $y \not\in S$ then $\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$
}
}
\caption{Game $\game{4}$ for the
proof of Theorem~\ref{thm:bf-correctness}.}
\label{fig:bf-correctness-games2}
\end{figure}
\hfill\qed
\end{proof}

>>>>

Note that $\game{4}(A)=1$ iff there are~$r$ queries to the
$\HashOracle$ oracle that increment~$\err$, i.e., queries $y \not\in
S$ such that $\bigwedge_{j=1}^{k} M[v_j]=1$.
%We can assume without
%loss of generality that~$A$ does not call~$\HashOracle$ on $y \in S$
%because the indices $v_1,v_2,\ldots,v_k$ that will correspond to any
%$y \not\in S$ will be \emph{independent} of those corresponding to
%any of the $y \in S$. Thus these queries are wasted.
There are at total of $q_T + q_H$ queries made to~$\HashOracle$,
either directly by~$A$ or indirectly when~$A$ calls~$\TestOracle$.
For $\game{4}(A)$ to return~1, there must be~$r$ among these that
increment~$\err$. %We can assume without loss of generality that~$A$
%halts as soon as~$\err=r$ (which it can easily track), so
There are $\binom{q_T+q_H}{r}$ possible ``winning'' query patterns
to consider.  \jnote{I changed the bound; I don't think it was
correct before.} As each error event is independent of all previous
choices made by the~$\HashOracle$, we need only consider the
probability of a single error. Using the upper bound on false
positives for the classical Bloom filter shown by Kirsch and
Mitzenmacher~\cite{kirsch2006less}, we have $\Prob{\game{4}(A)=1}
\leq \binom{q_T+q_H}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
We conclude that
\[
\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,,
\]
as claimed.
\begin{figure}[tp]
\fpage{.8}{
\hpagessl{.4}{.4}
{
\underline{$\game{4}(A)$} \\ %\fbox{$\game{5}(A)$}}\\
$S \getsr A$; $\err \gets 0$;  $\calC \gets \emptyset$\\
%$\mathcal{I}\getsr [\{1,2,\ldots,q_T+q_H\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
%if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(q_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
if $\Ans[x] = \undefined$\\
\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
Return $\Ans[x]$\\
%
}
{
\oracle{$\HashOracle(y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
%\nudge $c \gets c + 1$\\
%\nudge for $j \in \{1,2,\ldots,k\}$\\
%\nudge $v_j \getsr [m]$\\
%
$M \gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge if $M[v_j] \neq 1$ then \\
\nudge \nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
%\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
\nudge \nudge Return $\left(v_1,\ldots,v_k\right)$\\
%\nudge \nudge $\Break$\\
%if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
%if $c \notin \calI$ then $\bad \gets \true$\\
if $y \not\in S$ then $\err \gets \err +1$\\
$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
Return $\left(v_1,\ldots,v_k\right)$ } } \caption{Game $\game{4}$
for the proof of Theorem~\ref{thm:bf-correctness}. \jnote{The
centering/spacing are not right.}} \label{fig:bf-correctness-games2}
\end{figure}
\hfill\qed
\end{proof}

### 2016-12-14 ds-correctness.tex
Continuing my pass...

\medskip
\oracle{$\HashOracle(x)$}\\
for $j = 1$ to~$k$\\
\nudge $v_j \getsr [m]$\\
Return $\left(v_1,\ldots,v_k\right)$ } } \caption{Games
$\game{0}$--$\game{3}$ for the proof of
Theorem~\ref{thm:ds-correctness}.} \label{fig:ds-correctness-games}
\end{figure}

@@

\medskip
\oracle{$\HashOracle(x)$}\\
\nudge Return $\OK$, for $j\in[1,k]$ } {
$\adversaryv{D^\TestOracle}$\\[4pt]
On input $\emptystring$:\\
\nudge $S \getsr A$\\
\nudge Return~$S$\\
On input $\pubaux$:\\
\nudge $c \gets 0$, $\calC \gets \emptyset$, $\err \gets 0$\\
\nudge $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
\nudge Run $A(\pubaux)$\\
\nudge When $A$ asks $\qry_x$:\\
\nudge\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge\nudge $\calC \gets \calC \cup \{x\}$\\
\nudge\nudge $c \gets c+1$; $r \gets 0$\\
\nudge\nudge if $c \in \mathcal{I}$\\
\nudge\nudge \nudge $r \gets \TestOracle(\qry_x)$\\
\nudge\nudge Reply to~$A$ with $r$\\
\nudge When $A$ halts:\\
\nudge\nudge Return $\bot$ } } \caption{Left: Adversary $B$
simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
proof of Theorem~\ref{thm:ds-correctness}. Right: Adversary $D$ for
Theorem~\ref{thm:ds-correctness}.
}\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
%\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
\end{figure}

>>>>

\medskip
\oracle{$\HashOracle(x)$}\\
for $j = 1$ to~$k$\\
\nudge $v_j \getsr [m]$\\
Return $\left(v_1,\ldots,v_k\right)$ } } \caption{Games
$\game{0}$--$\game{3}$ for the proof of
Theorem~\ref{thm:ds-correctness}. \jnote{Centering seems off?}} \label{fig:ds-correctness-games}
\end{figure}

@@

\medskip
\oracle{$\HashOracle(x)$}\\
\nudge Return $\OK$, for $j\in[1,k]$ } {
$\adversaryv{D^\TestOracle}$\\[4pt]
On input $\emptystring$:\\
\nudge $S \getsr A$\\
\nudge Return~$S$\\
On input $\pubaux$:\\
\nudge $c \gets 0$, $\calC \gets \emptyset$, $\err \gets 0$\\
\nudge $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
\nudge Run $A(\pubaux)$\\
\nudge When $A$ asks $\qry_x$:\\
\nudge\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
\nudge\nudge $\calC \gets \calC \cup \{x\}$\\
\nudge\nudge $c \gets c+1$; $r \gets 0$\\
\nudge\nudge if $c \in \mathcal{I}$\\
\nudge\nudge \nudge $r \gets \TestOracle(\qry_x)$\\
\nudge\nudge Reply to~$A$ with $r$\\
\nudge When $A$ halts:\\
\nudge\nudge Return $\bot$ } } \caption{{\bf Left:} Adversary $B$
simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
proof of Theorem~\ref{thm:ds-correctness}. {\bf Right:} Adversary $D$ for
Theorem~\ref{thm:ds-correctness}.
}\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
%\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
\end{figure}

### 2016-12-14 results.tex
Continuing my pass...

\begin{theorem}%[\rm{SS-privacy of DS PRF}]
\label{thm:ds-ss} Fix $k,m,n>0$ and ~$\elts$, and let
$\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the domain-separated PRF
data structure.  Let $\leak(S)=|S|$. Then
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq
\AdvPRF{F}{B}\,.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
Let $\ell(n) = kn$. Let $\Rep_1$ be the algorithm that, on input a
set $S=\{x_1,\ldots,x_n\}$, outputs $\{\langle i,x_j \rangle\}_{i\in
{k}, j \in [n]}$. Let $\Rep_2$ be the algorithm that, on input
$n,y_1, \ldots, y_{\ell(n)}$, initializes an $m$-bit array $M$ to~0
and then sets $M[y_i] \gets 1$ for $i \in [\ell(n)]$. One can easily
verify that $(\Rep_1, \Rep_2, \ell, F)$ is a factoring of~$\Pi$.
Applying Theorem~\ref{thm:priv-ss} yields the claimed result.
\hfill\qed
\end{proof}

@@

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$B \gets \mathsf{bigram}(x)$\\
$\overline{M} \gets 0^m$\\
for each $b \in B$\\
\nudge for $j \in [k]$\\
\nudge\nudge $f_1 \gets F_{K}(\langle 1,b \rangle)$, $f_2 \gets F_{K}(\langle 2,b \rangle)$\\
\nudge\nudge $i \gets f_1+j\cdot f_2 \bmod m$\\
\nudge\nudge $\overline{M}[i] \gets 1$\\
if $\overline{M} \in \pubaux$ then Return 1 \\
Return 0
}
\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for the linear-PRF
  data structure $\setprim_{\mathrm{lin}}$ {\bf Right:}
The scheme from Niedermeyer et al.\cite{niedermeyer2014cryptanalysis}, $\setprim_{\bilin}$.
The $\mathsf{bigram}$ algorithm takes a
string~$x=x_1,x_2,\ldots,x_\ell$ as input, and returns the set of
bigrams for the left- and right-padded string $\sqcup x \sqcup$,
i.e. $\{\sqcup x_1, x_1x_2,\ldots,x_{\ell-1}x_\ell,x_\ell\sqcup\}$.
Both schemes use a function family $F\colon \calK \times \bits^* \to [m]$.
}\label{fig:lin-and-bi-lin}
\label{fig:niedermeyer}
\end{figure}

%JK
\subsection{Linear PRF-hash Bloom Filter }
%\heading{Linear-PRF construction. }
The domain-separated PRF-hash requires~$k$ PRF evaluations per
set-membership query, and this may be unattractive in certain use
cases.  Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown
that two PRF evaluations suffice, defining the hash functions to be
$h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle)
\bmod m$, where~$m$ is the bit-length of the Bloom
filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot
F_{K_2}(x) \bmod m$, using distinct keys instead of
domain-separation, but the constructions are equivalent with respect
to security.} We call this the \emph{linear PRF-hash} Bloom filter.
\jnote{Maybe call it ``Pairwise-independent hash''?} In this
section, we show that this scheme is both correct and private.

Looking ahead to the next section, we will analyze a closely related
construction, which was attacked by Niedermeyer et
al.~\cite{niedermeyer2014cryptanalysis} in the context of private
medical-record linkage.  It uses the same linear-PRF hash functions,
but has a $\Rep$ algorithm that that does not ensure that the hash
functions are called on \emph{distinct} values.  We show that this is
\emph{not} private with respect to our SS notion for a leakage
function that leaks nearly the entire set~$S$.
%\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Niedermeyer et al. violate.}

Taken together, the results of this section and the next highlight
the privacy of the linear PRF-hash construction can be sensitive to
its usage.

\heading{Correctness. }
For now, let $n,k,m \geq 0$.  Then $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-bi-lin} (left side).  The following result shows, informally, that if~$F$ is a good PRF, then $\setprim_{\mathrm{lin}}$ is correct against adaptive error-finding adversaries.

\begin{theorem}[{\rm Correctness of linear-PRF}]\label{thm1}\label{thm:lin-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bi-lin}.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
\end{theorem}
Again, Kirsch and Mitzenmacher~\cite{kirsch2006less} show
that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.
the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
The proof will appear in the full version, but we note that it very
closely follows the proof of correctness for the DS PRF-hash
construction, Theorem~\ref{thm:ds-correctness}.
%\input{lin-correctness}

\heading{Privacy. }
The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:priv-ss}.
\begin{theorem}[{\rm SS-privacy of linear-PRF}]\label{thm:lin-privacy}
Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}=
(\Rep, \Qry)$ be the set-membership data structure (over~$\elts$)
described in Figure~\ref{fig:lin-and-bi-lin}. For any set~$S \in
2^{\elts}$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and
an adversary~$B$ (making $2n$ queries) such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\;.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:priv-ss}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,\linebreak s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.  It returns~$M$ as $\pubaux$. \hfill\qed
\end{proof}

%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NIEDERMEYER")  %%%%%%%%%%%%%%%%%%%%
\subsection{Bigram Linear-PRF Construction}
%\heading{Bigram Linear-PRF construction (``Niedermeyer''). }
%\heading{Correctness.}
%\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
\heading{Privacy. } Consider the set-membership data structure given
in Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the
\emph{bigram linear-PRF} construction.  This construction is of
practical interest, as it has been suggested as a way to address the
privacy-preserving record-linkage problem, in particular for linking
common records in medical
databases~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
We only address the privacy of this construction, as the correctness
follows immediately from the correctness of the Linear-PRF
construction.  The privacy, however, does not.  Here we exhibit an
efficient SS-privacy attack even when simulator is provided nearly
the entire set.  Consider the following ``all-but-last'' leakage
function. On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns
$x'_n \gets x_n[1:|x_n|-1]$ and returns
$\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.

>>>>

\begin{theorem}%[\rm{SS-privacy of DS PRF}]
\label{thm:ds-ss} Fix $k,m,n>0$ and~$\elts$, and let
$\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the domain-separated PRF
data structure over~$\elts$.  Let $\leak(S)=|S|$. Then \jnote{Need
to rewrite theorem statement.}
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq
\AdvPRF{F}{B}\,.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
Let $\ell(n) = kn$, let $\Rep_1$ be the algorithm that, on input a
set $S=\{x_1,\ldots,x_n\}$, outputs $\{\langle i,x_j \rangle\}_{i\in
{k}, j \in [n]}$, and let $\Rep_2$ be the algorithm that, on input
$n,y_1, \ldots, y_{\ell(n)}$, initializes an $m$-bit array $M$ to~0
and then sets $M[y_i] \gets 1$ for $i \in [\ell(n)]$. One can easily
verify that $(\Rep_1, \Rep_2, \ell, F)$ is a factoring
of~$\Pi_{\mathrm{ds}}$. Applying Theorem~\ref{thm:priv-ss} yields
the claimed result. \hfill\qed
\end{proof}

@@

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$B \gets \mathsf{bigram}(x)$\\
$\overline{M} \gets 0^m$\\
for each $b \in B$\\
\nudge for $j \in [k]$\\
\nudge\nudge $f_1 \gets F_{K}(\langle 1,b \rangle)$, $f_2 \gets F_{K}(\langle 2,b \rangle)$\\
\nudge\nudge $i \gets f_1+j\cdot f_2 \bmod m$\\
\nudge\nudge $\overline{M}[i] \gets 1$\\
if $\overline{M} \in \pubaux$ then Return 1 \\
Return 0
}
\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for the linear-PRF
  data structure $\setprim_{\mathrm{lin}}$. {\bf Right:}
Data structure $\setprim_{\bilin}$ from Niedermeyer et
al.~\cite{niedermeyer2014cryptanalysis}. The $\mathsf{bigram}$
algorithm takes a string~$x=x_1,x_2,\ldots,x_\ell$ as input, and
returns the set of bigrams for the left- and right-padded string
$\sqcup x \sqcup$, i.e. $\{\sqcup x_1,
x_1x_2,\ldots,x_{\ell-1}x_\ell,x_\ell\sqcup\}$. Both schemes use a
function family $F\colon \calK \times \bits^* \to [m]$.
}\label{fig:lin-and-bi-lin} \label{fig:niedermeyer}
\end{figure}

\subsection{Linear PRF-hash Bloom Filter }
%\heading{Linear-PRF construction. }

\jnote{The BF, DS-PRF, and Linear PRF data structures are all the
same underlying construction but using different instantiations of
the hash functions. Can we just express them all as, e.g.,
$\Pi_{BF}(H_1, \ldots, H_k)$ with different choices for the~$H$'s?
Similarly, the names should be consistent; maybe ``RO Bloom
filter,'' ``independent-PRF Bloom filter,'' and
``pairwise-independent-PRF Bloom filter''?}

The domain-separated PRF data structure requires~$k$ PRF evaluations
per set-membership query.  Kirsch and
Mitzenmacher~\cite{kirsch2006less} studied a variant, which uses
just two PRF evaluations per query, in which the indices $h_j$ of
the array that get set for a given element $x$ are (essentially)
computed as $h_j = F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x
\rangle) \bmod m$ (where $m$ is the length of the array); see
Figure~\ref{fig:lin-and-bi-lin} (left side).
%shown that two PRF evaluations suffice, defining the hash functions
%to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x
%\rangle) \bmod m$, where~$m$ is the bit-length of the Bloom
%filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot
%F_{K_2}(x) \bmod m$, using distinct keys instead of
%domain-separation, but the constructions are equivalent with respect
%to security.}
We call this the \emph{linear PRF-hash} Bloom filter, and denote it
by $\setprim_{\mathrm{lin}}$. \jnote{Maybe call it
``Pairwise-independent hash''?} In this section, we show that this
scheme is both correct and private.

\jnote{I was not happy with the paragraph contrasting these results
with those of the next section. The attack on by Niedermeyer has
nothing to do with the hash functions used; it is due to the fact
that they work on bigrams.}
%Looking ahead, in the next section we
%will analyze a closely related construction that was attacked by
%Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis}. That
%construction computes indices $h_j$ in the same way, but does not
%ensure that $F$ is evaluated on \emph{distinct} values; that
%construction is \emph{not} private.
%\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Niedermeyer et al. violate.}
%This illustrates that the privacy of the linear PRF-hash
%construction can be sensitive to its usage.

\heading{Correctness. } The following result shows, informally, that
if~$F$ is a good PRF, then $\setprim_{\mathrm{lin}}$ is correct
against adaptive error-finding adversaries.

\jnote{Again, the theorem should not refer to specific adversaries,
but should instead refer to given resource bounds.}

\begin{theorem}%[{\rm Correctness of linear-PRF}]
\label{thm1}\label{thm:lin-correctness} Fix $k,m,n,r>0$ and~$\elts$,
and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the
set-membership data structure over~$\elts$.  For any adversary~$A$
that makes a total of~$q_T$ queries to its $\Test$ oracle and runs
in time~$t$, there exist~$B_1,B_2$ such that
\[
\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \cdot \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B_1$ and $B_2$ each ask~$q$ oracle queries and run in
time~$O(t+qm)$.
\end{theorem}
Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the ($r=1$,
zero-query) error-probability for~$\setprim_\mathrm{lin}$ is always
within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic rate
of convergence is faster than~$1/n$; the multiplicative term
$\binom{q}{r}$ arises due to switching from the zero-query setting
to the adaptive setting. A proof of the above will appear in the
full version, but we remark that it closely follows the proof of
Theorem~\ref{thm:bf-correctness}.
%\input{lin-correctness}

\heading{Privacy. } Simulation-based privacy of the linear PRF-hash
construction follows from~Theorem~\ref{thm:priv-ss}.

\begin{theorem}%[{\rm SS-privacy of linear-PRF}]
\label{thm:lin-privacy} Fix $k,m,n>0$ and $\elts$, and let
$\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data
structure over~$\elts$. Let $\leak(S)=|S|$.  Then \jnote{Need to
rewrite theorem statement.}
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\;.
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
Let $\ell(n) = 2n$, let $\Rep_1$ be the algorithm that, on input a
set $S=\{x_1,\ldots,x_n\}$, outputs $\{\langle b,x_i \rangle\}_{b\in
\{1,2\}, i \in [n]}$, and let $\Rep_2$ be the algorithm that, on
input $n,y_{1,1}, y_{2,1}, \ldots, y_{1,n}, y_{2,n}$,  initializes
an $m$-bit array $M$ to~0 and then sets $M[y_{1,i}+j \cdot y_{2,i}
\bmod m] \gets 1$ for $i \in [n]$ and $j \in [k]$. One can easily
verify that $(\Rep_1, \Rep_2, \ell, F)$ is a factoring
of~$\Pi_{\mathrm{ds}}$. Theorem~\ref{thm:priv-ss} yields the claimed
result. \hfill\qed
\end{proof}

%JK
%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NIEDERMEYER")  %%%%%%%%%%%%%%%%%%%%
\subsection{Bigram Linear-PRF Construction}
%\heading{Bigram Linear-PRF construction (``Niedermeyer''). }
%\heading{Correctness.}
%\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
Consider the set-membership data structure given in
Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the
\emph{bigram linear-PRF} construction.  This construction is of
practical interest, as it has been suggested as a way to address the
privacy-preserving record-linkage problem, in particular for linking
common records in medical
databases~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
\jnote{We should really give more discussion, explaining the goal of
``privacy-preserving record linkage'' and describing the protocol
(at a high level).}

\heading{Privacy. } We only address the privacy of this
construction, as the correctness follows immediately from the
correctness of the Linear-PRF construction.  The privacy, however,
does not.  Here we exhibit an efficient SS-privacy attack even when
simulator is provided nearly the entire set.  Consider the following
``all-but-last'' leakage function. On input a
set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets
x_n[1:|x_n|-1]$ and returns
$\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.
